### 2021-08-26 manuscript/conclusions.tex
Testes com dado real com grid irregular.

In this work, we were able to develop a fast equivalent layer technique for processing magnetic data with the method of Conjugate Gradient Least Square using the convolutional equivalent layer theory to obtain results of performance more than four orders of magnitude less than the classical equivalent layer. The sensitivity matrix of the magnetic equivalent layer carries the structure of BTTB matrices, which means a very low computational cost matrix-vector product and also the possibility to store only the first column of the matrix BCCB. In this work we propose a method to calculate the first six columns of the second derivatives matrices to embbed them into BCCB and then finally arrive in what would be the first column of the BCCB matrix embbeded from the sensitivity matrix.

@@

Real data test were also conducted in the region of Carajás, Pará, Brazil. With a regular grid of 2,500,000 observation points, store the full sensitivity matrix it would be necessary 45.47 Terabytes of RAM.  However, taking advantage symmetric or skew-symmetric matrices structures, it is possible to reconstruct the whole sensitivity matrix using only 114.44 Megabytes.
Using 50 iterations of the CGLS method took $15.5$ seconds and very good results of property estimative were obtained. Also the upward continuation transformation was successfull with good results and taking only $0.49$ seconds.

>>>>

In this work, we were able to develop a fast equivalent layer technique for processing magnetic data with the method of Conjugate Gradient Least Square using the convolutional equivalent layer theory to obtain results of performance more than four orders of magnitude less than the classical equivalent layer. The sensitivity matrix of the magnetic equivalent layer carries the structure of BTTB matrices, which means a very low computational cost matrix-vector product and also the possibility to store only the first column of the matrix BCCB. In this work we propose a novel method to use only one equivalent source and calculating the first six columns of the inverse of distance second derivatives matrices to arrive in the first column of the BCCB matrix embbeded from the original magnetic kernel sensitivity matrix.

@@

Real data test were also conducted in the region of Carajás, Pará, Brazil. With an irregular grid of $1,310,000$ observation points, store the full sensitivity matrix it would be necessary $12.49$ Terabytes of RAM.  However, taking advantage of the symmetric or skew-symmetric matrices structures, it is possible to reconstruct the whole sensitivity matrix using only $59.97$ Megabytes.
Using 200 iterations of the CGLS method took $385.56$ seconds and very good results of property estimative were obtained. Also the upward-continuation transformation showed good results and took only $2.64$ seconds.

### 2021-08-26 manuscript/methodology.tex
Testes com dado real com grid irregular.

The combination of the main field and crustal field is known as internal field or total-field. Taking the difference between this internal field and the main field given by a model (e.g. IGRF), at the same location, we have the total-field anomaly.

@@

@@

\subsection{Structure of the components matrices $\mathbf{H_{xy}}$}

>>>>

The combination of the main field and crustal field is known as internal field or total-field. Taking the difference between the main field given by a model (e.g. IGRF) and this internal field, at the same location, we have the total-field anomaly.

@@

%======================================================================================
\subsection{Conjugate Gradient Least Square method convergence criteria}
%======================================================================================

In theory, this method is bound to converge at $N$ iterations maximum, but in a later part of this work we show with numerical results that the convergence is much faster for the linear system we are solving. Setting a minimum tolerance of the residuals is a good option to carry out this algorithm efficiently and still obtaining very good results. Another possibility is to set an invariance to the euclidian norm of residuals between iteractions, wich would increase algorithm runtime, but with smaller residuals. We chose the first option, as we achieve satisfatory results.

@@

%======================================================================================
\subsection{Structure of the components matrices $\mathbf{H_{xy}}$}
%======================================================================================

### 2021-08-26 manuscript/synthetic_data.tex
Testes com dado real com grid irregular.

In figure \ref{fig:convergence_synthetic_mag} we have the convergence analysis of the CGLS method to estimate the equivalent sources parameter vector $\mathbf{d}(\hat{\mathbf{p}})$ used for this synthetic test. The squared euclidian norm of residuals decreases as expected, with good results at 50 iterations, stabilizing afterwards. This result shows that it is not necessary to run the conjugate gradient least square method at $N$ iterations to get a theoretically exactly solution (which in practice would never occur due to roundoff errors), as this could be very demanding to process even with a small layer with $N = 6,\, 400$ equivalent sources. Setting a minimum tolerance of the residuals is a good option to carry out this algorithm efficiently and still obtaining very good results. Another possibility is to set an invariance to the euclidian norm of residuals between iteractions, wich would increase algorithm runtime, but with smaller residuals. We chose the first option, as we achieve satisfatory results.

>>>>

In figure \ref{fig:convergence_synthetic_mag} we have the convergence analysis of the CGLS method to estimate the equivalent sources parameter vector $\mathbf{d}(\hat{\mathbf{p}})$ used for this synthetic test. The squared euclidian norm of residuals decreases as expected, with good results at 50 iterations, stabilizing afterwards. This result shows that it is not necessary to run the conjugate gradient least square method at $N$ iterations to get a theoretically exactly solution (which in practice would never occur due to roundoff errors), as this could be very demanding to process even with a small layer with $N = 6,\, 400$ equivalent sources.
